### 2014-08-03 tex/GAME_HARD_01_CONTRIBUTION.tex
Added order of magnitude comparison elaboration under section Results.

% CONTRIBUTION - RESULTS
\subsection{Results}
\label{sec:contribution:results}
Considering the average percentage decreases in execution time of $99.8-99.9\%$ presented in table~\ref{tab:contribution:results:summaryint}~and~\ref{tab:contribution:results:summaryfloat}; results indicate significant improvements in the performance of both kernels when using WARP, compared to that of the the reference~device~driver.
These improvements, accounting for well-over two orders of magnitude, induce an execution time spanning tenths of milliseconds; a considerable advance from that of roughly ten entire seconds.

In terms of memory latency, table~\ref{tab:contribution:results:summaryint} demonstrates performance gains with the hardware accelerated Subject (when utilizing shared memory amongst blocks), with varying results for the other Subjects; either increasing or decreasing execution time (see table~\ref{tab:contribution:results:summaryfloat}).
As such, applicable to both integer- and floating point-precision, the performance of WARP is impaired by the kernel utilizing shared memory.
In the Microsoft guide on WARP~\citeweb[]{warp}, the author claims that an application tuned to run efficiently on hardware will run efficiently whilst simulated using WARP as well - and vice versa.
However, the data collected for this study rather indicates an over $20\%$ percentual increase in execution time, independant of precision, even though the same kernel accelerates the hardware accelerated Subject by roughly $70$\%.
This demonstrates that that the capabilities of WARP do not extend to memory latency optimization by utilization of lower-latency shared memory.
The floating point scenario of this effect is visualized in figure~\ref{fig:contribution:results:warp:msswarp}.

>>>>

% CONTRIBUTION - RESULTS
\subsection{Results}
\label{sec:contribution:results}
Considering the average percentage decreases in execution time of $99.8$ to $99.9\%$ (presented in table~\ref{tab:contribution:results:summaryint}~and~\ref{tab:contribution:results:summaryfloat}); results indicate significant improvements in the performance of both kernels when using WARP, compared to that of the the reference~device~driver.
These improvements, accounting for three orders of magnitude on average, induce an execution time spanning tenths of milliseconds; a considerable advance from that of roughly ten seconds.
The measurements indicate that the reference~device~driver is $4$~to~$5$ orders of magnitude slower than the hardware accelerated reference case, depending on whether or not the kernel utilizes shared memory to accelerate memory accesses on the video card.
Meanwhile, the WARP device driver performs but $1$~to~$2$ orders of magnitude worse than hardware acceleration, also depending on shared memory utilization.

In terms of memory latency, table~\ref{tab:contribution:results:summaryint} demonstrates performance gains with the hardware accelerated Subject (when utilizing shared memory amongst blocks), with varying results for the other Subjects; either increasing or decreasing execution time (see table~\ref{tab:contribution:results:summaryfloat}).
As such, applicable to both integer- and floating point precision, the performance of WARP is impaired by the kernel utilizing shared memory.
In the Microsoft guide on WARP~\citeweb[]{warp}, the author claims that an application tuned to run efficiently on hardware will run efficiently whilst simulated using WARP as well - and vice versa.
However, the collected data rather indicate a roughly $20\%$ percentual increase in execution time, independant of precision, even though the same kernel accelerates the hardware accelerated Subject by roughly $70$\%.
This demonstrates that that the capabilities of WARP do not extend to memory latency optimization by lower-latency shared memory.
The floating point scenario of this effect is visualized in figure~\ref{fig:contribution:results:warp:msswarp}.
